% !TEX root = ../ui-thesis.tex
% !TeX program = xelatex


\AbstractEn{
  The rise of content creation has led to an unprecedented demand for high-quality, copyright-free music for use in multimedia content. Lo-fi music, with its calming and soothing properties, has become a staple in video, podcast, and live stream production. However, obtaining high-quality, copyright-free lo-fi music can be a challenging and costly process. This paper presents a novel approach to generating lo-fi music using a small language model, addressing the need for a cost-effective and scalable solution for content creators. We utilize the RWKV architecture, a state-of-the-art model that combines the efficiency of a transformer with the flexibility of a recurrent neural network.
  In this paper, we focus on the technical aspects of generating lo-fi music, exploring the challenges of training a model to produce high-quality music of unlimited length. We trained two separate models, one for piano and one for drum instruments, to generate lo-fi music on demand. Our approach enables content creators to focus on their creative vision, rather than spending time and resources searching for suitable music.
  By automating the process of music generation, we aim to reduce the importance of music selection in content creation, freeing creators to focus on their core competencies. Our work has far-reaching implications for the music industry, enabling the efficient creation of high-quality content and paving the way for new forms of creative expression.
}

\KeywordsEn{
  1- generate lo-fi music
  2- music generating ai
  3- generate ai
}